---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
library(locatexec)
```

# locatexec

<!-- badges: start -->
[![R build status](https://github.com/ardata-fr/locatexec/workflows/R-CMD-check/badge.svg)](https://github.com/ardata-fr/locatexec/actions)
[![Lifecycle: maturing](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
<!-- badges: end -->

The package aims to allow the localization of external programs such as
"python", "Google Chrome", "node.js" and "LibreOffice" in order to be able to
easily call them from R.

This makes it easier to call these programs from R from various operating
systems.

```{r}
library(locatexec)

if(exec_available("node"))
  message(node_exec())

if(exec_available("npm"))
  message(npm_exec())

if(exec_available("chrome"))
  message(chrome_exec())

if(exec_available("firefox"))
  message(firefox_exec())

if(exec_available("python"))
  message(python_exec())

if(exec_available("pip"))
  message(pip_exec())

if(exec_available("libreoffice"))
  message(libreoffice_exec())

if(exec_available("word"))
  message(word_exec())

if(exec_available("powerpoint"))
  message(powerpoint_exec())

if(exec_available("excel"))
  message(excel_exec())
```

## Motivations

This was motivated by the need for tools
similar to `rmarkdown::pandoc_available()` and `rmarkdown::pandoc_exec()` but
allowing to locate external programs other than `pandoc`. 

I need to use these programs from R without having heavy dependencies. These
functions will mainly be used to automate some visual tests or to improve the
documentation of other packages.


## Installation

You can install the development version from GitHub with:

``` r
# install.packages("devtools")
devtools::install_github("ardata-fr/locatexec")
```

## Related work

* Packages pagedown is providing `find_chrome()` for finding "Google Chrome".

* If you want to go deeper with 'R' and 'node.js', I recommend 
package [packer](https://packer.john-coene.com/).

* If you want to go deeper with 'R' and 'Python', I recommend 
package [reticulate](https://rstudio.github.io/reticulate/).

