---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
library(locatexec)
```

# locatexec

<!-- badges: start -->
[![R build status](https://github.com/ardata-fr/locatexec/workflows/R-CMD-check/badge.svg)](https://github.com/ardata-fr/locatexec/actions)
[![version](https://www.r-pkg.org/badges/version/locatexec)](https://CRAN.R-project.org/package=locatexec)
[![codecov test coverage](https://codecov.io/gh/ardata-fr/locatexec/branch/main/graph/badge.svg)](https://app.codecov.io/gh/ardata-fr/locatexec)
<!-- badges: end -->

The package helps locate external programs such as
"python", "Google Chrome", "node.js" and "LibreOffice" so that they can be
called easily from R.

This makes it easier to call these programs from R across various operating
systems.

```{r}
library(locatexec)

if(exec_available("node")){
  message(exec_version("node"))
  message(node_exec())
}
```

```{r echo=FALSE}
execs <- c("node", "chrome", "python", "libreoffice", "excel", "powerpoint",
"pip", "firefox", "npm", "word", "air", "pandoc")
exec_cmd <- paste0(execs, "_exec")

dat <- data.frame(
  exec = execs,
  exec_fun = paste0("`", exec_cmd, "()`"),
  available = vapply(execs, exec_available, FUN.VALUE = FALSE),
  version = vapply(execs, function(exec) format(exec_version(exec)), FUN.VALUE = NA_character_),
  stringsAsFactors = FALSE, row.names = NULL)

path <- character(nrow(dat))
path[dat$available] <- sapply(
  exec_cmd[dat$available], 
  function(cmd){
    do.call(cmd, list())
  })
path[!dat$available] <- NA_character_
dat$path <- path
knitr::kable(dat)
```

## Motivations

This was motivated by the need for tools
similar to `rmarkdown::pandoc_available()` and `rmarkdown::pandoc_exec()` but
allowing to locate external programs other than `pandoc`. 

I needed to call these programs from R without pulling in heavy dependencies.

## Installation

You can install the CRAN version with:

``` r
install.packages("locatexec")
```

## Related work

* Package pagedown provides `find_chrome()` for finding "Google Chrome".

* Package findpython provides `find_python_cmd()` for finding "python".

* If you want to go deeper with 'R' and 'node.js', I recommend 
package [packer](https://packer.john-coene.com/).

* If you want to go deeper with 'R' and 'Python', I recommend 
package [reticulate](https://rstudio.github.io/reticulate/).

